%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {CLOUD ENGiNEER} % Job title
    {Teamwork} % Organization
    {Moka, Mauritius} % Location
    {Febuary 2024 ‑ Present} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {CLOUD ENGiNEER} % Job title
    {Rapp} % Organization
    {Phoenix, Mauritius} % Location
    {Febuary 2023 ‑ Febuary 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {EDeployed infrastructure on Azure using Terraform, including provisioning and configuring Azure Functions, Azure Web App services ADF, APIM,
        Azure Monitoring, and Dashboards}
        \item {Created and managed a user‑friendly CI/CD pipeline on Azure DevOps, allowing developers to deploy their Node.js applications.}
        \item {Containerized a Node.js application using Docker and stored the Dockerfile in Azure Repos.}
        \item {Deployed infrastructure on AWS using Terraform.}
        \item {Implemented AWS Serverless Application Model (SAM) to deploy Lambda functions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SYSTEM ADMiNiSTRATOR} % Job title
    {Lottech LTD} % Organization
    {Ebene, Mauritius} % Location
    {August. 2022 ‑ January. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted daily inspections of the data center facility to ensure proper functioning of equipment, infrastructure, and environmental conditions.}
        \item {Orchestrated quarterly disaster recovery exercises by initiating the planned shutdown of the main datacenter and seamlessly switching opera‑
        tions to the backup datacenter.}
        \item {Conducted post‑exercise reviews and gathered feedback to identify areas for improvement and optimize the disaster recovery plan.}
        \item {Verified the integrity and availability of backup systems, such as uninterruptible power supplies (UPS), generators, and redundant network
        connections.}
        \item {Developed and implemented Python scripts to automate daily tasks, increasing productivity and efficiency within the team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LINUX SYSTEM ADMiNiSTRATOR} % Job title
    {Linkbynet} % Organization
    {Phoenix, Mauritius} % Location
    {October 2020 ‑ August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responding to and resolving assigned tickets in the IT operations ticket queue.}
        \item {Monthly customer facing Linux/Windows server administration tasks that include disk space maintenance, security updates, and OS upgrades.}
        \item {Utilized Terraform to provision and manage VMs on multiple cloud platforms, including Azure, AWS, and VMware.}
        \item {Used Ansible to automate configuration management tasks on Linux servers, ensuring consistent and efficient provisioning, installation, and
        configuration of software and services.}
        \item {Upgrade from McAfee to SentinelOne on Windows and Linux servers, enhancing endpoint protection capabilities and ensuring advanced secu‑
        rity measures.}
        \item {Developed a Python script for efficient data extraction from APIs and automated data integration into Excel files.}
        \item {Provided customer support services.}
        \item {Created and managed DNS records on AWS Route 53.}
        \item {Created comprehensive technical documentation(SOP), detailing system configurations, processes, procedures, and best practices, to facilitate
        knowledge sharing and ensure clear and concise information for team members.}
        \item {Provided mentorship and guidance to newcomers and interns, offering support, sharing knowledge.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ceridian} % Job title
    {APPLiCATiON ANALYST} % Organization
    {Ebene, Mauritius} % Location
    {June 2019 ‑ Febuary 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Apply technical knowledge and expertise to provide support services to clients, ensuring delivery of solutions according to agreed schedules
        and standards}
        \item {Communicate effectively to deliver excellent customer service, providing support via email and phone.}
        \item {Escalate risks or issues to Team Lead or Lead Engineer as needed to ensure project delivery schedules are met.}
        \item {Demonstrate proficiency in computer skills, SQL, SQL Server and software development concepts.}
        \item {Meet SLAs (Service Level Agreements) to ensure client satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
